Paper 1 Analysis

### 2016-06-16 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Fixed misspelling.

<<rho_1-PT-reample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Bootstrap resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP. The ``x'' indicates location of base model value.">>=
fancy_scientific <- function(l) {
     # turn in to character string in scientific notation
     l <- format(l, scientific = TRUE)
     # quote the part before the exponent to keep all the digits
     l <- gsub("^(.*)e", "'\\1'e", l)
     # turn the 'e+' into plotmath format
     l <- gsub("e", "%*%10^", l)
     # return this as an expression
     parse(text=l)
}

>>>>

<<rho_1-PT-resample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Bootstrap resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP. The ``x'' indicates location of base model value.">>=
fancy_scientific <- function(l) {
     # turn in to character string in scientific notation
     l <- format(l, scientific = TRUE)
     # quote the part before the exponent to keep all the digits
     l <- gsub("^(.*)e", "'\\1'e", l)
     # turn the 'e+' into plotmath format
     l <- gsub("e", "%*%10^", l)
     # return this as an expression
     parse(text=l)
}
